Reading text files

### 2021-09-30 text/Rmd/map-projections/index.Rmd
Moved files out of monthly folders

---
title: "Blog post: Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

>>>>

---
title: "Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

### 2021-09-30 text/Rmd/misuse-of-gradient/index.Rmd
Moved files out of monthly folders

---
title: "Blog post: An example of a poor color choice"
author: "Steve Simon"
source: "New"
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

>>>>

---
title: "An example of a poor color choice"
author: "Steve Simon"
source: "New"
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

### 2021-09-30 text/Rmd/quasi-likelihood/index.Rmd
Moved files out of monthly folders

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: "New"
date: "2020-09-20"
categories:
- Blog post
tags:
- Gneralized linear model
output: html_document
---

>>>>

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: "New"
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

### 2021-09-30 text/Rmd/reading-text-files/index.Rmd
Moved files out of monthly folders

---
title: "Reading text files"
author: "Steve Simon"
source: "New"
date:2020-04-30"
categories: Blog post
tags: Data management
output: html_document
---

>>>>

---
title: "Reading text files"
author: "Steve Simon"
source: "New"
date: "2020-04-30"
categories:
- Blog post
tags:
- Data management
output: html_document
---
